An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/motiv.tex
add Example 4

\para{Example~4: Singular Value Errors} 
A common error is that a value is set too high or too low.
For example, consider the following:
This should be the singular value error.
We need an example from Stack Overflow to illustrate the 
real-world problem. I guess the buffer size example is fine.

>>>>

\para{Example~4: Singular Value Errors} 
A common error is that a value is set too high or too low.
For example, a parameter relating to memory might be too large,
exhausting the RAM and causing extreme slowness. 
Consider the following real-world misconfiguration file \cite{singleValue}: the
user was experiencing the ``My SQL Server has gone away" error.  
She had the following line in her configuration file.

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_allowed_packet = 100M
\end{lstlisting}

The user resolved the issue by replacing the above line with {\tt max\_allowed\_packet=20M}. 
It turns out that the original value, 100 MB, is extremely large, a  
statistically anomalous value for the {\tt max\_allowed\_packet} attribute. ConfigV can detect these
outliers. Run on the user's original configuration file, ConfigV would output:

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
WARNING: Violated Upper Hampel Rule for max_allowed_packet with value 104857600 
\end{lstlisting}

In the above, 104857600 represents the integer value of 100 megabytes.
